Appendix

### 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd
fix file paths to metadata, change plot base size, make contingnecy plot appear

In this paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames. Next, we report how the proportion of faces and hands changes with age in each of the three children in the dataset. We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.

@@

# Results
## Access to social information across age

```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face/hands detection within frames where frames/ were detected." }
face_hand_contingency_plot <- ggplot(face_hand_contingency, 
       aes(x=age_day_bin, y=prop, 
           col=child_id)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion joint hand/face detection') + 
  xlab('Age (Months)') +
  theme_few(base_size=12) +
  facet_grid(~region) +
  # scale_color_manual(values = c( "#DAA0EE","#710D93"), name="") +
  scale_color_brewer(palette="Dark2") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=12)) 
```

## Variability in social information across learning contexts 
```{r}
load(here::here('data/data_preprint/saycam_metadata.RData')) # meta

@@

ggplot(all_to_plot, aes(x = Location, y = mean, col=region)) + 
  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.6)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.6)) +
  coord_flip() + 
  ylab('Proportion Detected')+
  xlab('')+
  theme_few(base_size=18) +
  theme(legend.position = "bottom") +
  facet_grid(.~child_id)  +
  scale_size_continuous(name = "Detections (Log 10)") +
  scale_linetype_manual(values=c("solid", "dashed","solid","dashed"), name = "") +
  scale_color_manual(values = c("#268bd2", "#51acec", "#dc322f","#ea5e5c"), name = "") +
  theme(legend.text=element_text(size=8))

>>>>

In this paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames. 
Next, we report how the proportion of faces and hands changes with age in each of the three children in the dataset. 
We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development.

@@

# Results
## Access to social information across age
```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face/hands detection within frames where frames/ were detected." }
ggplot(face_hand_contingency, 
       aes(x=age_day_bin, y=prop, 
           col=child_id)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion joint hand/face detection') + 
  xlab('Age (Months)') +
  theme_few(base_size=12) +
  facet_grid(~region) +
  # scale_color_manual(values = c( "#DAA0EE","#710D93"), name="") +
  scale_color_brewer(palette="Dark2") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=12)) 
```

## Variability in social information across learning contexts 
```{r}
load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta

@@

ggplot(all_to_plot, aes(x = Location, y = mean, col=region)) + 
  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.6)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.6)) +
  coord_flip() + 
  ylab('Proportion Detected')+
  xlab('')+
  theme_few(base_size=12) +
  theme(legend.position = "bottom") +
  facet_grid(.~child_id)  +
  scale_size_continuous(name = "Detections (Log 10)") +
  scale_linetype_manual(values=c("solid", "dashed","solid","dashed"), name = "") +
  scale_color_manual(values = c("#268bd2", "#51acec", "#dc322f","#ea5e5c"), name = "") +
  theme(legend.text=element_text(size=8))
